---
title: "A Description of R Package 'dhh'"
author: "Runlong Tang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A Description of R Package 'dhh'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The name of this R package "dhh" can be understood as "Distributions with Heavy Heads". The probability density function of the heavy-headed distribution is 
$$f(x) = \frac{\alpha (b-a)^{-\alpha}}{(x-a)^{1-\alpha}}I\{a<x<b\},$$
with parameters $a<b$ and $\alpha>0$. For the motivation and derivation of this distribution, please see the references.

This package contains four functions on a heavy-headed distribution: 

* `dhh`: the probability density function
* `phh`: the cumulative distribution function (CDF)
* `qhh`: the quantile function
* `rhh`: the random variables

Next, I will introduce these functions with examples.

To use this library, we can first install it and then use the following command.
```{r}
library(dhh)
```


## On `dhh`
This function `dhh(x, a, b, alpha)` gives the values of the density of the heavy-headed distribution.

The default values of `a`, `b` and `alpha` are `0`, `1` and `0.1`, respectively.  Then, the following two commands give the same result, the value of the density at `0.5`.
```{r}
dhh(0.5)
dhh(0.5, 0, 1, 0.1)
```

The argument `x` can be a vector.
```{r}
dhh(c(0.5, 0.7))
```

We can take a look at the plots of some density functions.
```{r, fig.show='hold'}
curve(dhh(x, a=0, b=1, alpha=0.1), -1, 2)
curve(dhh(x, a=0, b=10, alpha=0.1), -1, 11)
```


## On `phh`
This function `phh(x, a, b, alpha)` gives the values of the CDF of the heavy-headed distribution.

The default values of `a`, `b` and `alpha` are `0`, `1` and `0.1`, respectively.  Then, the following two commands give the same result, the value of the density at `0.5`.
```{r}
phh(0.5)
phh(0.5, 0, 1, 0.1)
```

The argument `x` can be a vector.
```{r}
phh(c(0.5, 0.7))
```


We can take a look at the plots of some CDF's.
```{r, fig.show='hold'}
curve(phh(x, a=0, b=1, alpha=0.1), -1, 2)
curve(phh(x, a=0, b=10, alpha=0.1), -1, 11)
```

## On `qhh`
This function `qhh(p, a, b, alpha)` gives the quantiles of the heavy-headed distribution.

The default values of `a`, `b` and `alpha` are `0`, `1` and `0.1`, respectively.  Then, the following two commands give the same result, the value of the density at `0.5`.
```{r}
qhh(0.9)
qhh(0.9, a=0, b=1, alpha=0.1)
```

The argument `p` can be a vector.
```{r}
phh(qhh((1:9)/10))
```

We can take a look at the plots of some quantile functions.
```{r, fig.show='hold'}
curve(qhh(x, 0, 1, 0.1), from = 0.1, to = 0.9)
curve(qhh(x, a=10, b=100, alpha = 0.1), from = 0.1, to = 0.9)
```

## On `rhh`
This function `rhh(n, a, b, alpha1)` generate $n$ i.i.d. random variables following the heavy-headed distribution.

The default values of `a`, `b` and `alpha` are `0`, `1` and `0.1`, respectively.  Then, the following two commands are the same.
```{r}
rhh(5)
rhh(5, a = 0, b = 1, alpha = 0.1)
```

We can generate $10000$ i.i.d. random variables and plot the histogram. Then we can add the density plot.
```{r}
hist(rhh(10000), freq=FALSE)
curve(dhh, add = TRUE, col = 2)
```

We can also check the fact that the density goes to infinity as `a` goes to `a`.
```{r}
dhh(c(0.1, 0.01, 0.001, 0.0001, 0.00001))
```


## References
Runlong Tang (2018) A Note On Finite Moments, Rediscovery Of The Pareto Distribution and Distributions With Heavy Tails and Heads
(v1) <https://sites.google.com/site/tangrunlong/notes-on-finance>



